Partial Differential Equations

### 2015-12-26 pde/transforms.tex
working on PDE

\subsubsection{The Fourier Sine Transform}

>>>>

\subsubsection{The Fourier Sine and Cosine Transform}
Much like the Fourier series, the Fourier transform can also be split into a sine and cosine
transform. The rules for the transformation still hold; we are still only concerned with the
position variable $x$. The transform for the positional derivatives do change however. We have
the following:
\[
\Four_{s}[f(x)] = \frac{2}{\pi}\int_{0}^{\infty}\sin{(\omega x)}f(x)\mathop{dx}
\qquad\qquad\qquad
\Four_{c}[f(x)] = \frac{2}{\pi}\int_{0}^{\infty}\cos{(\omega x)}f(x)\mathop{dx}
\]
Applying these definitions to our positional derivatives yields
\begin{alignat*}{3}
&\Four_{s}[u_{x}(x,t)] = -\omega\Four_{c}[u(x,t)] \qquad\qquad\qquad\qquad\qquad
&&\Four_{c}[u_{x}(x,t)] = -\frac{2}{\pi}u(0,t)+\omega\Four_{s}[u(x,t)]\\
&\Four_{s}[u_{xx}(x,t)] = \frac{2\omega u(0,t)}{\pi} + \omega^{2}\Four_{s}[u(x,t)]
&&\Four_{c}[u_{xx}(x,t)] = -\frac{2}{\pi}u_{x}(0,t)-\omega^{2}\Four_{c}[u(x,t)]
\end{alignat*}
Notice that with the transform of the first derivative, we end up with the opposite transform of the
original function. Let's look at an example.

\noindent \textbf{\textit{Ex:}} Solve the following PDE using a Fourier Transform.
\[
% \begin{cases*}
2u_{x} + 3u_{t} = 0
% u(0,t) = 3
% \end{cases*}
\]
\indent \textbf{\textit{Solution:}} We will start with the sine transform. Applying the sine transform to
both sides of the equation yields
\begin{gather*}
2\Four_{s}[u_{x}] + 3\Four_{s}[u_{t}] = \Four_{s}[0]\\
-2\omega\Lambda(\omega,t) + 3\Lambda_{t}(\omega,t) = 0\\
-2\omega\Lambda + 3\Lambda' = 0
\end{gather*}
This is a first order ODE that we can easily solve. We get a final solution of
\[
\Lambda(\omega,t) = f(t)e^{-\frac{2}{3}\omega}
\]
And we are done.
